---
title: 'Homework 1 - Research in Health Economics'
author: "Alexia Witthaus Viñé"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
    toc_depth: '2'
  prettydoc::html_pretty:
    df_print: kable
    highlight: vignette
    theme: lumen
  html_document:
    df_print: paged
---
```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(lemon)
knit_print.data.frame <- lemon_print
library(tidyverse)
library(readr)
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE, fig.width = 16/2, fig.height = 9/2, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```

```{r}
full_ma_data <- read_rds("data/output/full_ma_data.rds")
```


# Question 1 

```{r}
paste0("There are ", nrow(full_ma_data), " observations in my current dataset")
```


# Question 2 

```{r}
# do -1 because there is one of the 27 is NA, and that doesn't correspond to a plan, ask to do with the NAs
paste0("There are ", length(unique(full_ma_data$plan_type)) -1, " unique plan types in the dataset")
```

# Question 3

```{r render=lemon_print}
# q_3_df <- full_ma_data %>% 
#   group_by(year, plan_type)%>% 
#   summarize(n_under_plan_type = n())%>% 
#   spread(year, n_under_plan_type)

read_rds("results/q_3_df.rds")
```

# Question 4 
```{r}
#filter for snp and for 800 series plan 
# full_ma_data2 <- full_ma_data %>% 
#                   filter(snp == 'No' | !(planid %in% 800:899))
```



```{r render=lemon_print}
# q_4_df <- full_ma_data2 %>% 
#   group_by(year, plan_type)%>% 
#   summarize(n_under_plan_type = n()) %>% 
#   spread(year, n_under_plan_type)

read_rds("q_4_df.rds")
```

# Question 5 

```{r}
# contract_service_area<- read_rds("data/output/contract_service_area.rds")
```

```{r}
#Should I work with the filtered data here? 
# joined_df <- left_join(full_ma_data2, contract_service_area ,by = c("contractid", "fips", "year"))
```

```{r}
#What is meant by restrict dataset ot contracts that are approved by respective counties? Given the left join, do we have to change anything in regards to restricting the data? 
# joined_df %>% 
#   filter(!is.na(avg_enrollment))%>%
#   group_by(year, county.x)%>% 
#   summarize(avg_prem = mean(avg_enrollment, na.rm = TRUE))%>% 
#   group_by(year)%>% 
#   summarize(avg = mean(avg_prem))%>%
#   ggplot(aes( x = year, y  = avg))+
#   geom_line()+
#   labs( title = 'Average of enrollees per county', x = 'Year', y = 'Number of enrollees')+
#   theme_minimal()
#How is approved by respective counties mean? What does non-missing enrollment data mean? 
```


```{r}
library(png)
readPNG("results/Q5_Graph.png")
```
I tried to read the image in but it wouldn't work/give me error


# Question 6 

```{r}
# penetration_data <- read_rds("data/output/ma_penetration.rds")
# premium_data <- read_rds ("data/output/plan_premiums.rds")
```

```{r}
# joined_df2 <- left_join(premium_data, penetration_data, by = c("state", "county", "year"))
```

```{r}
# joined_df3 <- left_join(joined_df, joined_df2, by = c("fips",  "year", "contractid", "county.x" = "county", "ssa.x" = "ssa"))
```
I got this completely wrong. Joined to the worng thing and gave me error

```{r}
# joined_df3 %>% 
#   group_by(year)%>% 
#   summarize(prem = mean(premium, na.rm = TRUE))%>%
#   ggplot( aes(year, prem))+
#   geom_line(color = 'red')+
#   labs( title = 'Average premium over time', x = 'Year', y = 'Average Premium')+
#   theme_minimal()
```

# Question 7 

```{r}
# joined_df3 %>% 
#   filter(!is.na(premium))%>% 
#   group_by(year)%>% 
#   summarize(perc_0 = ((sum(premium == 0))/n())* 100)%>% 
#   ggplot( aes(year, perc_0))+
#   geom_line(color = 'blue')+
#   labs( title = 'Percentage of $0 Premium Plans over time', x = 'Year', y = 'Percentage of $0 Premium Plans')+
#   theme_minimal()
  
```

# Question 8 



# Question 9 



# Question 10 

Working with this data was at times a little frustrating, since I was not really familiar with the data, and what the end goal was. I was not really working  and doing all these things with a goal in mind, but instead I was simply following instructions, which made it harder for me to understand the purpose of the assingment and what I was supposed to achieve with it, and consequently at times I didn't know what I was doing.

