---
title: "Homework 1 - Research in Health Economics"
author: "Alexia Witthaus Viñé"
date: "2023-01-29"
output: pdf_document
---
```{r, warning = FALSE, echo = FALSE, message = FALSE}
load("Hwk1_workspace.Rdata")
library(lemon)
knit_print.data.frame <- lemon_print
library(tidyverse)
library(readr)
library(imputeTS)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, fig.width = 16/2, fig.height = 9/2, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```


# Question 1 

There exist `r format(nrow(full.ma.data), big.mark = ",")` observations in my dataset. 

# Question 2 

There exist `r length(unique(full.ma.data$plan_type)) -1 ` different data types

# Question 3 

```{r, render = lemon_print}
q_3_df <- na_replace(q_3_df, 0)
q_3_df <- q_3_df[-27,]
q_3_df
```

# Question 4 
```{r, render = lemon_print}
q_4_df<- na_replace(q_4_df, 0)
q_4_df<- q_4_df[-17,]
q_4_df
```

# Question 5 

```{r}
graph_q5
```


# Question 6 

```{r}
graph_q6
```


# Question 7 

```{r}
graph_q7
```

# Question 8 

800-series plans are plans offered to employer and group union group sponsors. I believe we might have removed these observations from the dataset, since these might not be representative from a Medicare user. 

# Question 9 

So many plans charge a $0 premium, because it is an additional premium to pay in addition to the Plan B premium. Government funding pays insurers to allow this to happen, and for beneficiaries this means that there might be higher out-of pocket costs, or that other benefits such as certain prescription drug coverage are not included. 

# Question 10 

For me, working with the data was a little frustrating, especially since at the beginning, I didn't really know what I was doing. The first data set took very long to run, and I am not used to working with datasets that are so big. Once I started working with the data (once I did this right), the dataset becamse more manageble and easier to work with. 


